|

### 2023-01-22 paper_comparison/paper_comparison/paper_comparison.Rmd
modify the different distribution plot

  # Combined with data for shape 1
  bind_rows(dat_shape_1) %>%
  VI_MODEL$plot() +
  facet_wrap(~shape, scales = "free_x", labeller = label_parsed, ncol = 4) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())
```

@@

# Data for uniform distribution
ori_dat <- poly_model(shape = 1, 
                      x = {
                        raw_x <- rand_uniform(-1, 1);
                        closed_form(~stand_dist(raw_x))
                        }, 
                      sigma = 0.5)$gen(300)

# Plot the data for uniform distribution
dp1 <- VI_MODEL$plot(ori_dat) + 
  ggtitle("A. Uniform") + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for normal distribution
dp2 <- poly_model(shape = 1, 
                  x = {
                    raw_x <- rand_normal(sigma = 0.3); 
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 0.5)$
  gen(300, computed = select(ori_dat, e)) %>%
  VI_MODEL$plot() +
  ggtitle("B. Normal") +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for lognormal distribution
dp3 <- poly_model(shape = 1, 
                  x = {
                    raw_x <- rand_lognormal(sigma = 0.6);
                    closed_form(~stand_dist(raw_x/3 - 1))
                    }, 
                  sigma = 0.5)$
  gen(300, computed = select(ori_dat, e)) %>%
  VI_MODEL$plot() +
  ggtitle("C. Skewed") +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for discrete uniform distribution
dp4 <- poly_model(shape = 1, 
                  x = {
                    raw_x <- rand_uniform_d(k = 5, even = TRUE);
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 0.5)$
  gen(300, computed = select(ori_dat, e)) %>%
  VI_MODEL$plot() +
  ggtitle("D. Discrete") +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

patchwork::wrap_plots(dp1, dp2, dp3, dp4, ncol = 4)
```

>>>>

  # Combined with data for shape 1
  bind_rows(dat_shape_1) %>%
  VI_MODEL$plot() +
  facet_wrap(~shape, scales = "free", labeller = label_parsed, ncol = 4) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())
```

@@

# Data for uniform distribution
dat_dist_1 <- poly_model(shape = 1, 
                      x = {
                        raw_x <- rand_uniform(-1, 1);
                        closed_form(~stand_dist(raw_x))
                        }, 
                      sigma = 0.5)$gen(300) %>%
  mutate(x_dist = "Uniform")

# Generate data for other distributions
dat_dist_2 <- poly_model(shape = 1,
                         x = {
                           raw_x <- rand_normal(sigma = 0.3); 
                           closed_form(~stand_dist(raw_x))
                           }, 
                         sigma = 0.5)$
  gen(300, computed = select(dat_dist_1, e)) %>%
  mutate(x_dist = "Normal")

dat_dist_3 <- poly_model(shape = 1,
                         x = {
                           raw_x <- rand_lognormal(sigma = 0.6); 
                           closed_form(~stand_dist(raw_x/3 - 1))
                           }, 
                         sigma = 0.5)$
  gen(300, computed = select(dat_dist_1, e)) %>%
  mutate(x_dist = "Skewed")

dat_dist_4 <- poly_model(shape = 1,
                         x = {
                           raw_x <- rand_uniform_d(k = 5, even = TRUE); 
                           closed_form(~stand_dist(raw_x))
                           }, 
                         sigma = 0.5)$
  gen(300, computed = select(dat_dist_1, e)) %>%
  mutate(x_dist = "Discrete")

# Generate and plot data for discrete uniform distribution
bind_rows(dat_dist_1, dat_dist_2, dat_dist_3, dat_dist_4) %>%
  VI_MODEL$plot() +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank()) +
  facet_wrap(~x_dist, ncol = 4, scales = "free")
```
